Experiment 1 Analysis

### 2023-07-24 Analysis/e1_Analysis.qmd
minor org

>>>>

```{r}
# non linear learning models

# Fit the model
model <- lmer(
  dist ~ vb * condit + 
    (1 | id) + 
    (1 + gt.train | id:condit), 
 # family = binomial(link = "logit"), 
  data = e1[e1$expMode=="train",]
)

model <- lmer(
  vx ~ vb * condit + I(gt.train^2) + 
    (1 + gt.train + I(gt.train^2) | id:condit), 
  data = e1[e1$expMode=="train",]
)

summary(model)

e1$gt.train.scaled <- scale(e1$gt.train)
# Fit the model with the rescaled variables
model <- lmer(
  dist ~ vb * condit + I(gt.train.scaled^2) + 
    (1 + gt.train.scaled + I(gt.train.scaled^2) | id:condit), 
  data = e1[e1$expMode=="train",]
)
summary(model)

library(nlme)

# Define a non-linear function for the learning effect
learning_effect <- function(time, Asym, R0, lrc) {
  Asym + R0 * exp(-exp(lrc) * time)
}

# Fit the model
model <- nlme(
  vx ~ learning_effect(gt.train.scaled, Asym, R0, lrc) * condit,
  fixed = Asym + R0 + lrc ~ 1,
  random = Asym + R0 ~ 1 | id,
  start = c(Asym = 1, R0 = 1, lrc = 0),
  data = e1[e1$expMode=="train",]
)

e1$condit_numeric <- as.numeric(e1$condit)

# Fit the model
model <- nlme(
  vx ~ learning_effect(gt.train.scaled, Asym, R0, lrc) * condit_numeric,
  fixed = Asym + R0 + lrc ~ 1,
  random = Asym + R0 ~ 1 | id,
  start = c(Asym = 1, R0 = 1, lrc = 0),
  data = e1[e1$expMode=="train",]
)
summary(model)

model <- nlme(
  # Reflects the shift in velocity across conditions and time
  vx ~ learning_effect(gt.train.scaled, Asym, R0, lrc) * condit_numeric,
  # Fixed effects structure
  fixed = Asym + R0 + lrc ~ 1,
  # Random effects structure, now includes 'lrc' for individual learning rates
  random = Asym + R0 + lrc ~ 1 | id,
  # Starting values for the parameters
  start = c(Asym = 1, R0 = 1, lrc = 0),
  # Subset of the data used for training phase
  data = e1 %>% filter(expMode=="train")
)

# Prints out a summary of the model
summary(model)
